My title

### 2024-03-16 paper/paper.qmd
Edits

Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

We can use maths by including latex between dollar signs, for instance $\theta$.

>>>>

Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand. In practice `rstanarm` converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `modelsummary` package of @modelsummary and `here` package of @here. We use the default priors from `rstanarm`.

@@
